Phonon polaritonics in two-dimensional materials

### 2019-03-19 paper.tex
stuff before change to achemso format

Before moving on to analyze the electrodynamics of 2D phonon polaritons, we make three comments on lack of LO--TO splitting in 2D polar materials. The first is that this situation is in stark contrast to the situation of polar materials in 3D, which have a finite LO--TO splitting at the $\Gamma$ point. In the absence of such LO--TO splitting in 3D, there would be no frequency compatible with the existence of a phonon  polariton. On the contrary, we will show that in 2D, despite the absence of LO--TO splitting at the $\Gamma$ point, there persists a strongly confined evanescent electromagnetic mode with a high local density of states which in all respects is similar to a phonon polariton of a thin film, but is in fact the 2D LO phonon of the polar monolayer (thus the phrases ``phonon polariton'' and ``2D LO phonon'' may be used somewhat interchangeably as is the case in plasmonics where the terms ``plasmon polariton'' and ``2D plasmon'' are often used interchangeably).

@@

\addition{%
Analogously, our considerations can be extended to 1D polar materials, such as BN nanotubes, by employing the 1D Coulomb interaction (and, naturally, the 1D-specific eigendisplacements).
For a 1D system of transverse extent $R$ (\eg, the radius of a nanotube), the 1D Coulomb interaction is $e^2K_0(qr)/2\pi\epsilon_0$, where $K_0$ is the (zeroth order) modified Bessel function of the second kind. 
Thus, the $q$-dependence of the (squared) LO--TO splitting is $q^2K_0(qR)\simeq - q^2 \log q R$. 
This closely mirrors the situation in 1D plasmonics, as expected from the discussion of Figure 1. 
%As regards the optical properties, the optical conductivity is still governed by Eq.~\eqref{eq:2dsusceptibility}.
}

@@

While we have focused on anomalies between the atomically-thin limit of bulk and a true monolayer, a comparison of the monolayer with the fundamental phonon polariton mode of the one-atom-thick thin film suggests that we have a reasonable qualitative understanding of the monolayer dispersion from the one-atom-thick thin film. 
%
\addition{%
This qualitative similarity is to be somewhat expected, as a 2D layer can be considered as a very thin film of bulk material, provided that the microscopic properties of the bulk and monolayer do not deviate substantially. 
The differences between the $t = t_{\text{2D}} = \SI{0.33}{\nm}$ bulky thin-film and monolayer that nevertheless do exist, reflect such microscopic deviations.
Occasionally, \eg for compatibility with standard numerical tools, it is useful to introduce a fictitious, effective bulk material whose fundamental thin-film mode \emph{exactly} matches the monolayer's. 
The dielectric function of such a ``bulkified'' monolayer is thickness-dependent and anisotropic: for a film in the $xy$ plane, it is $\boldsymbol{\epsilon}_{\text{Q2D}} = (\hat{\mathbf{x}}\hat{\mathbf{x}} + \hat{\mathbf{y}}\hat{\mathbf{y}})\epsilon_{\text{Q2D}, \parallel} + \hat{\mathbf{z}}\hat{\mathbf{z}}\epsilon_{\text{Q2D}, \perp}$ with $\epsilon_{\text{Q2D}, \perp} = 1$ and
\begin{equation}
	\epsilon_{\text{Q2D}, \parallel}(\omega) = 1 + \frac{1}{t}\frac{4\epsilon_{\mathrm{env}}\omega_{\mathrm{TO}}v_\mathrm{g}}{\omega^2-\omega_{\mathrm{TO}}^2+\iu\omega\tau^{-1}}.
\end{equation}
}

>>>>

Before moving on to analyze the electrodynamics of 2D phonon polaritons, we make three comments on lack of LO--TO splitting in 2D polar materials. The first is that this situation is in stark contrast to the situation of polar materials in 3D, which have a finite LO--TO splitting at the $\Gamma$ point. In the absence of such LO--TO splitting in 3D, there would be no frequency compatible with the existence of a phonon  polariton. On the contrary, we will show that in 2D, despite the absence of LO--TO splitting at the $\Gamma$ point, there persists a strongly confined evanescent electromagnetic mode with a high local density of states which in all respects is similar to a phonon polariton of a thin film, but is in fact the 2D LO phonon of the polar monolayer (thus the phrases `phonon polariton' and `2D LO phonon' may be used somewhat interchangeably as is the case in plasmonics where the terms `plasmon polariton' and `2D plasmon' are often used interchangeably).

@@

\addition{%
Analogously, our considerations can be extended to 1D polar materials, such as BN nanotubes, by employing the 1D Coulomb interaction (and, naturally, the 1D-specific eigendisplacements).
For a 1D system of transverse extent $R$ (\eg, the radius of a nanotube), the 1D Coulomb interaction is $e^2K_0(qR)/2\pi\epsilon_0$, where $K_0$ is the (zeroth order) modified Bessel function of the second kind. 
Thus, the $q$-dependence of the (squared) LO--TO splitting in 1D is $q^2K_0(qR)\simeq - q^2 \log q R$. 
This parallels the situation in 1D plasmonics, as expected from the discussion of Figure 1. 
%As regards the optical properties, the optical conductivity is still governed by Eq.~\eqref{eq:2dsusceptibility}.
}

@@

While we have focused on anomalies between the atomically-thin limit of bulk and a true monolayer, a comparison of the monolayer with the fundamental phonon polariton mode of the one-atom-thick thin film suggests that we have a reasonable qualitative understanding of the monolayer dispersion from the one-atom-thick thin film. 
%
\addition{%
This qualitative similarity is to be somewhat expected, as a 2D layer can be considered as a very thin film of bulk material, provided that the microscopic properties of the bulk and monolayer do not deviate substantially. 
The differences between the $t = t_{\text{2D}} = \SI{0.33}{\nm}$ bulk thin-film and monolayer that nevertheless do exist, reflect such microscopic deviations.
Occasionally, \eg for compatibility with standard numerical tools, it is useful to introduce a fictitious, effective bulk material whose fundamental thin-film mode \emph{exactly} matches the monolayer's. 
The dielectric function of such a ``bulkified'' monolayer is thickness-dependent and anisotropic: for a film in the $xy$ plane, it is $\boldsymbol{\epsilon}_{\text{Q2D}} = (\hat{\mathbf{x}}\hat{\mathbf{x}} + \hat{\mathbf{y}}\hat{\mathbf{y}})\epsilon_{\text{Q2D}, \parallel} + \hat{\mathbf{z}}\hat{\mathbf{z}}\epsilon_{\text{Q2D}, \perp}$ with $\epsilon_{\text{Q2D}, \perp} = 1$ and
\begin{equation}
	\epsilon_{\text{Q2D}, \parallel}(\omega) 
	=
	 1 + \frac{\iu\sigma}{\varepsilon_0\omega t} 
 	=
	 1 + \frac{1}{t}\frac{4\epsilon_{\mathrm{env}}\omega_{\mathrm{TO}}v_\mathrm{g}}{\omega^2-\omega_{\mathrm{TO}}^2+\iu\omega\tau^{-1}}.
\end{equation}
}
